Exploring Determinants of Child Mortality Globally (2022): The Role of Vaccination, Healthcare Spending, and Nutrition

### 2024-11-28 paper/paper.qmd
combine libraries

library(tidyverse)
```

@@

# Load necessary libraries
library(ggplot2)
library(arrow)

@@

# Load necessary libraries
library(ggplot2)
library(arrow)
library(knitr)

@@

# Load necessary libraries
library(ggplot2)
library(arrow)
library(knitr)
library(dplyr)

@@

#### Load libraries ####
library(tidyverse)
library(rstanarm)
library(knitr)
library(arrow)
library(modelsummary)

>>>>

library(tidyverse)
library(ggplot2)
library(arrow)
library(knitr)
library(dplyr)
library(modelsummary)
library(rstanarm)
```

@@

@@

@@

@@
